IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/intro.tex
caps
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  information flow control language.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Section~\ref{sec:retrofit})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism, and show a class of restrictions on
  the IFC language that preserves non-interference. (Section~\ref{sec:formal})
  \item We connect our formal semantics to real implementations of
  coarse-grained IFC systems for Javascript and Haskell, and explain
  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
  \item We briefly describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, privileges, or a
  notation of clearance. (Section~\ref{sec:extensions})
  \item We informally relate our results to a monadic interpretation
      of IFC which guided our design. (Section~\ref{sec:monad})     
\end{itemize}

>>>>

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  information flow control language.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Section~\ref{sec:retrofit})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism, and show a class of restrictions on
  the IFC language that preserves non-interference. (Section~\ref{sec:formal})
  \item We connect our formal semantics to real implementations of
  coarse-grained IFC systems for JavaScript and Haskell, and explain
  how our system could be used to enforce IFC in C. (Section~\ref{sec:real})
  \item We briefly describe ways to enrich the core IFC language with
  more advanced concepts such as labeled values, privileges, or a
  notation of clearance. (Section~\ref{sec:extensions})
  \item We informally relate our results to a monadic interpretation
      of IFC which guided our design. (Section~\ref{sec:monad})     
\end{itemize}
